%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.3, 10 May 2020) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 and academicon fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}
\usepackage{setspace}
\usepackage[default]{lato}


% Change the colours if you want to
\definecolor{Black}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
% \colorlet{name}{black}
\colorlet{tagline}{Black}
\colorlet{heading}{Black}
\colorlet{headingrule}{Black}
\colorlet{accent}{Black}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
% \renewcommand{\namefont}{\Huge\rmfamily\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\newcommand{\cvtagsmall}[1]{\cvtagx{\footnotesize{#1}}}

\begin{document}
\name{Vikram Singh}
\tagline{University of Pennsylvania}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%% You can add multiple photos on the left or right
% \photoL{2cm}{Yacht_High,Suitcase_High}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \href{mailto::singhvik@sas.upenn.edu}{\email{singhvik@sas.upenn.edu}}
%   \phone{000-00-0000}
  \location{Hong Kong}
  \href{https://www.linkedin.com/in/vikram-singh-2002/}{\linkedin{vikram-singh-2002}}
  \href{https://github.com/vsingh18567}{\github{vsingh18567}}
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
  % \orcid{0000-0000-0000-0000}
  %% You can add your own arbtrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}
  %% Or you can declare your own field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
  % \gitlab{your_id}
}

\makecvheader

Freshman studying Mathematics \& Computer Science. Looking for internship opportunities in Software Engineering and Data Science. 

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}
% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

\cvsection{Experience}

\cvevent{Backend Developer}{Penn Labs \href{https://github.com/pennlabs}{\github{}} \href{https://pennlabs.org/}{\homepage{}}}{Feb 2021 -- }{Philadelphia, PA}
\begin{itemize}
\item Create software used by thousands of faculty and students at the University of Pennsylvania.
\item Work on the Platform team, integrating all of PennLabs' products into one system. 
\end{itemize}
\divider

\cvevent{Data Scientist}{Wharton Analytics Fellows}{Sep 2020 -- Nov 2020}{Remote}
\begin{itemize}
\item Worked with SaaS Healthcare company with the aim of reducing customer churn. Used machine learning techniques to create a churn prediction model and identify key indicators of churn. 
\item Independently built Flask API to productionize model \& presented findings to company.
\end{itemize}

\divider

\cvevent{Summer Intern}{Rupifi}{Jun 2020 -- Jul 2020}{Remote}
\begin{itemize}
\item Studied the API documentation of Fintech companies to find trends in the types of services offered, and the tools provided to allow for easy integration.  
\end{itemize}

\divider


\cvsection{Projects}

\cvproject{FM Analytics \href{https://github.com/vsingh18567/FMAnalytics}{\github{}}
\href{https://fmanalytics.herokuapp.com/}{\homepage{}}\cvtagsmall{Python} \cvtagsmall{Django} \cvtagsmall{Web Dev}}
\begin{itemize}
  \item Web-app that allows players of the Football Manager (FM) video-game series to upload their game data and have it stored and analysed. 
  \item Deployed on Heroku
\end{itemize}

\divider 

\cvproject{Web Blog \href{https://github.com/vsingh18567/vsinghBlog}{\github{}\cvtagsmall{Python} \cvtagsmall{Django} \cvtagsmall{Web Dev}}}

\begin{itemize}
  \item Basic blog application that allows for CRUD operations on blog posts and handles user authentication
\end{itemize}
\divider
\cvproject{Minesweeper \href{https://github.com/vsingh18567/minesweeper}{\github{}}\cvtagsmall{Java}\cvtagsmall{Swing}}

\begin{itemize}
  \item Implementation of the traditional Minesweeper game using the Java Swing GUI library. Implements the Model-View-Controller GUI structure, File I/O and the recursive flood-fill algorithm. 
\end{itemize}
\divider
\cvproject{Coronavirus Tracker \href{https://github.com/vsingh18567/CoronavirusTracker}{\github{}}\cvtagsmall{Python}\cvtagsmall{Web Scraping}}
\begin{itemize}
  \item Script that scrapes Worldometer's Coronavirus data everyday and sends an e-mail with an update.  
\end{itemize}

% use ONLY \newpage if you want to force a page break for
% ONLY the currentc column

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Skills}
\cvtag{Python} \cvtag{Data Analysis} \cvtag{Pandas} \cvtag{Django} \cvtag{Numpy} \cvtag{Scikit-learn} \cvtag{Java} \cvtag{Swing} \cvtag{JavaScript} \cvtag{\LaTeX} \cvtag{OCaml} \cvtag{Git}

\divider

\cvtag{Leadership} \cvtag{Public Speaking / Debate} \cvtag{Adaptability} \cvtag{Commitment} \cvtag{Integrity}

\cvsection{Education}

\cveventx{Bachelor of Arts}{University of Pennsylvania}{2020 -- }{First-semester GPA: 4.0/4.0}
\begin{itemize}
  \item Intending to major in Mathematics \& Computer Science
  \item Relevant Coursework (including Spring 2021):
\end{itemize}

\cvtagsmall{Programming Techniques I-II}\cvtagsmall{Hon. Calculus II-III}\cvtagsmall{Maths of Computer Science}\cvtagsmall{Probability}

\divider

\cveventx{IB Diploma}{German Swiss International School}{2011 -- 2020}{43/45}
\begin{itemize}
  \item Higher-Level subjects: Mathematics, Economics, Physics
  \item ACT: 36/36
\end{itemize}

\cvsection{Activities}
\begin{itemize}
  \item Deputy Vice-President, Undergraduate Statistics Society
  \item Head Student and Head of Student Council, German Swiss International School
  \item Semi-finalist or better at six debate tournaments across Asia, Top 10 speaker at five tournaments.
  \item High-school Varsity Tennis Team Captain, Top 50 ranked junior in Hong Kong
\end{itemize}

\cvsection{Hobbies}
\begin{itemize}
  \item Rock music
  \item Soccer \& Tennis
  \item Global Affairs
\end{itemize}

\end{paracol}

\end{document}